---
title: "VIS_AND_EDA, ggplot 1"
author: "Xinyuan Liu"
date: "2021/10/5"
output: github_document
---

```{r}
library(tidyverse)
library(viridis)
library(patchwork)
library(ggridges)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## start with a familiar one

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y =tmax, color = name)) +
  geom_point(alpha = .3) +
  labs(
    title = "Temperature at three stations",
    x = "minimum daily temp(C)",
    y = "maximum daily temp(C)",
    caption = "Data from rnaaa package with three stations"
  ) + 
  scale_x_continuous(
    breaks =c(-15, 0, 15),
    labels = c("-15C", "0", "15C")
  ) + 
  scale_y_continuous(
    trans = "sqrt", 
    position = "right"
  ) +
  scale_color_hue(
    name = "location",
    h = c(100, 300)
    ) +
  scale_color_viridis_d() +
  theme_minimal() +
  theme(legend.position = "bottom")
  
```

## set option
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

## data in geoms

```{r}
central_park = 
  weather_df %>% 
  filter(name == "CentralPark_NY")
 
waikiki = 
  weather_df %>% 
  filter(name == "Waikiki_HA")

ggplot(data = waikiki, aes(x = date, y = tmax, color = name)) +
  geom_point()+
  geom_line(data = central_park)
```

## Patchwork

```{r}
ggp_tmax_tmin = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3)+
  theme(legend.position = "none")

ggp_prcp_dens = 
  weather_df %>% 
  filter(prcp > 0) %>%
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha =.3) +
  theme(legend.position = "none")

ggp_tmax_date =
  weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point() +
  geom_smooth() +
  theme(legend.position = "bottom")

(ggp_tmax_tmin + ggp_prcp_dens) / ggp_tmax_date
```

## data manipulation

```{r}
weather_df %>% 
  mutate(
    name = fct_reorder(name, tmax)
  ) %>% 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

what about tmax and tmin?

```{r}
weather_df %>% 
  pivot_longer(
    tmax:tmin,
    names_to = "obs",
    values_to = "temperature"
  ) %>% 
  ggplot(aes(x = temperature, fill = obs))+
  geom_density(alpha = .3) +
  facet_grid(. ~ name)
```

```{r}
pulse_df = 
  haven::read_sas("public_pulse_data.sas7bdat") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    values_to = "bdi", 
    names_prefix = "bdi_score_"
    ) %>% 
  mutate(visit = recode(visit, "bl" = "00m"))

pulse_df %>% 
  ggplot(aes(x = visit, y = bdi)) +
  geom_boxplot()
```
pulse_df %>% 
  ggplot(aes(x = visit, y = bdi)) +
  geom_point(size = .2) +
  geom_line(aes(group = id))
